Title Goes Here

### 2024-03-08 analysis/paper/paper.qmd
exploring smoothers

ggsave(here("analysis",
            "figures", 
            "fig-how-many-jobs-per-year.png"),
       bg ="white")
```

@@

```{r}
#| label: documents-requested

jobdata %>% 
  select(starts_with("documents_requested")) %>% 
  pivot_longer(everything()) %>% 
  group_by(name, value) %>% 
  tally() %>% 
  mutate(value = case_when(
    value == "Not requested in the job ad" ~ 0,
    value == "One" ~ 1,
    value == "Two (e.g. two syllabi)" ~ 2,
    value == "Three" ~ 3,
    .default = 0
  )) %>% 
  ggplot() +
  aes(value,
      n) +
  geom_col() +
  facet_wrap( ~ name) 
```

@@

ggplot(jobdata_requirements_means) +
  aes(year_ad_posted, 
      mean_n,
      group = name) +
  geom_line(linewidth = 2) +
  geom_jitter(data = jobdata_requirements,
             aes(year_ad_posted, 
                 value),
             alpha = 0.1,
             height = 0.2,
             width =  0.1) +
  facet_wrap(~name,
             scales = "free_y") +
  xlab("Year") +
  ylab("Number requested in job ad") +
  scale_y_continuous(breaks = integer_breaks()) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))

@@

ggplot() +
    geom_jitter(data = jobdata_requirements_by_rank,
                  aes(position_title, 
                      value),
                height = 0.05,
                alpha = 0.1) +
    geom_point(data = jobdata_requirements_by_rank_means,
               aes(position_title,
                   mean),
               size = 4,
               colour = "red") +
  facet_wrap( ~ name,
              scales = "free_y")
```

@@

@@

ggplot() +
  geom_line(data =  jobdata_geo_year_tally,
            aes(year_ad_posted,
                 prop,
                 group = name,
                 colour = name),
            size = 2,
            position=position_jitter(w=0.05, h=0.0)) +
   geom_point(data = jobdata_geo_year_tally_max,
              aes(year_ad_posted,
                  prop,
                  group = name,
                  colour = name),
              size = 5) +
   geom_text_repel(data = jobdata_geo_year_tally_max,
             aes(year_ad_posted,
                 prop ,
                 group = name,
                 colour = name,
                 label = name),
             nudge_y = 0.01,
             bg.color = "white",
             bg.r = 0.25,
             size = 3) +
  xlab("Year") +
  ylab("Proportion of all ads") +
  theme_minimal()

@@

ggplot() +
  geom_line(data =  jobdata_topic_year_tally,
            aes(year_ad_posted,
                prop,
                group = name,
                colour = name),
            size = 2,
            position=position_jitter(w=0.05, h=0.0)) +
  geom_point(data = jobdata_topic_year_tally_max,
             aes(year_ad_posted,
                 prop,
                 group = name,
                 colour = name),
             size = 10) +
  geom_text_repel(data = jobdata_topic_year_tally_max,
                  aes(year_ad_posted,
                      prop ,
                      group = name,
                      colour = name,
                      label = name),
                  nudge_y = 0.01,
                  bg.color = "white",
                  bg.r = 0.25,
                  size = 3) +
  xlab("Year") +
  ylab("Proportion of all ads") +
  theme_minimal()

>>>>

ggsave(here("analysis",
            "figures", 
            "fig-how-many-jobs-per-year.png"),
       height = 7,
       width = 22,
       bg ="white")
```

@@

@@

ggplot(jobdata_requirements_means) +
  aes(year_ad_posted, 
      mean_n,
      group = name) +
  geom_smooth(linewidth = 2,
              colour = "black") +
  geom_jitter(data = jobdata_requirements,
             aes(year_ad_posted, 
                 value),
             alpha = 0.1,
             height = 0.2,
             width =  0.1) +
  facet_wrap(~name,
             scales = "free_y") +
  xlab("Year") +
  ylab("Number requested in job ad") +
  scale_y_continuous(breaks = integer_breaks()) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))

@@

ggplot() +
    geom_jitter(data = jobdata_requirements_by_rank,
                  aes(position_title, 
                      value),
                height = 0.05,
                alpha = 0.1) +
    geom_point(data = jobdata_requirements_by_rank_means,
               aes(position_title,
                   mean),
               size = 4,
               colour = "red") +
  facet_wrap( ~ name,
              scales = "free_y") +
  theme_minimal()
```

@@

# BM TODO: check for job ads that have a location, but we're not getting it

@@

ggplot() +
  geom_smooth(data =  jobdata_geo_year_tally,
            aes(year_ad_posted,
                 prop,
                 group = name,
                 colour = name),
            size = 2,
           se = FALSE #,
           # position=position_jitter(w=0.05, h=0.0)
           ) +
   geom_point(data = jobdata_geo_year_tally_max,
              aes(year_ad_posted,
                  prop,
                  group = name,
                  colour = name),
              size = 5) +
   geom_text_repel(data = jobdata_geo_year_tally_max,
             aes(year_ad_posted,
                 prop ,
                 group = name,
                 colour = name,
                 label = name),
             nudge_y = 0.01,
             bg.color = "white",
             bg.r = 0.25,
             size = 3) +
  xlab("Year") +
  ylab("Proportion of all ads") +
  theme_minimal()

@@

ggplot() +
  geom_smooth(data =  jobdata_topic_year_tally,
            aes(year_ad_posted,
                prop,
                group = name,
                colour = name),
            size = 2,
           # position=position_jitter(w=0.05, h=0.0),
            se = FALSE) +
  geom_point(data = jobdata_topic_year_tally_max,
             aes(year_ad_posted,
                 prop,
                 group = name,
                 colour = name),
             size = 10) +
  geom_text_repel(data = jobdata_topic_year_tally_max,
                  aes(year_ad_posted,
                      prop ,
                      group = name,
                      colour = name,
                      label = name),
                  nudge_y = 0.01,
                  bg.color = "white",
                  bg.r = 0.25,
                  size = 3) +
  xlab("Year") +
  ylab("Proportion of all ads") +
  theme_minimal()
